\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-02-25 papers/itsc_2012/draft2.tex
simple but vital clarification to paper

\commentd{is this clear now? it's not a multigraph and there are no loops, since
  edges are lanes and turns. I have to think a bit about intersections as
  vertices strictly, though...}

A map is represented as a directed graph with \emph{lanes} and \emph{turns} as edges and
\emph{intersections} as vertices. A \emph{road} groups one or two groups of
lanes together, each group being a different direction of travel. Intersections
map the possible turns from incoming to outgoing lanes. Since both lanes and
turns support traffic, they are grouped together as the \emph{traversables} or
edges, meaning they have some total length.

>>>>

A map is represented as a directed graph with \emph{lanes} as edges and
\emph{turns} as vertices. A \emph{road} groups one or two groups of lanes
together, each group being a different direction of travel.
\emph{Intersections} map the possible turns from incoming to outgoing lanes.
Since both lanes and turns support traffic, they are grouped together as the
\emph{traversables}, meaning they have some geometric total length.
